---
title: "Electric_Vehicle_Project"
output: html_document
date: "2024-09-10"
---

# Specify the file path


```{r}
file_path <- "C:/Users/Shweta/Downloads/Electric Vehicle Population Data (1).csv"
```

# Read the CSV file into a data frame


```{r}
Electric_Vehicle_Population_Data <- read.csv(file_path)
```

# Display the first few rows of the data frame to confirm it was read correctly

head(Electric_Vehicle_Population_Data)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
is.null(Electric_Vehicle_Population_Data)
```
## Dataset cleaning for NULL values

```{r}
Electric_Vehicle_Population_Data %>%
  select(VIN, County, City, State, ZIP_Code, Model_Year, Make, Model, Electric_Vehicle_Type, CAFV, Range_Km, Base_MSRP, Legislative_District, DOLVehicleID, VehicleLocation, ElectricUtility) %>% na.omit()
```

```{r}
is.null(Electric_Vehicle_Population_Data)
```

##Calculating the Count of Electric Vehicle Type{BEV/PHEV} Per City and Arranging in Decreasing Order

```{r}
NEW_TABLE <- Electric_Vehicle_Population_Data %>% count(City , Electric_Vehicle_Type , sort = TRUE)
NEW_TABLE
```

##Calculating the count of Make{Brand} and Electric Vehicle Type{BEV/PHEV} per State and arranging in decreasing order.

```{r}
NEW_TABLE2 <- Electric_Vehicle_Population_Data %>% count(State , Make ,Electric_Vehicle_Type, sort = TRUE)
NEW_TABLE2
```
##Calculating the Count of Make{Brand} and Electric Vehicle Type{BEV/PHEV} per Year and arranging in decreasing order.

```{r}
NEW_TABLE3 <- Electric_Vehicle_Population_Data %>% count(Model_Year , Make ,Electric_Vehicle_Type, sort = TRUE)
NEW_TABLE3
```

##Calculating the Count of individual Make{Brand} per City with respect to its Model Year and arranging in descending order.

```{r}
NEW_TABLE4 <- Electric_Vehicle_Population_Data %>% count(City , Make , Model_Year, sort = TRUE)
NEW_TABLE4
```
##To show the preference of Electric Vehicle Type{BEV/PHEV} in Cities and taking the Top 20 Count.

```{r} 
NEW_TABLE %>% 
   slice(1:20) %>% 
ggplot(., aes(x= City, y = n, color = Electric_Vehicle_Type)) + 
  geom_bar (stat = 'identity') + 
labs (title ="ELECTRIC VEHICLE TYPE PER CITY") + 
  theme (axis.text.x=element_text (angle = -90, hjust = 0))
```

##To show which Make{Brands} increased the Production of Electric Vehicle Type{BEV/PHEV} per Year.
## TO SHOW TOP PREFERED ELECTRIC VEHICLE MANUFACTURING MAKE (BRANDS} IN TOP 40 CITIE PER YEAR. 
```{r}
ggplot(data = NEW_TABLE3, mapping = aes(x = Make, y = Model_Year, size = n, color = Electric_Vehicle_Type)) + 
geom_point() + 
labs(title = "Electric Vehicles type increase per Brand with respect to year") + 
  theme (axis.text.x=element_text (angle = -90, hjust = 0))
```

##To show the preference of Make{Brands} and Electric Vehicle Type{BEV/PHEV} in each State.
```{r}
ggplot(NEW_TABLE2, aes(Electric_Vehicle_Type, State, color = Make, size = Year)) + 
 geom_boxplot(size = 1)+
 labs(title = "Statewise increase in Electric Vehicle Type with respect to Brand")
```

## TO SHOW TOP PREFERED ELECTRIC VEHICLE MANUFACTURING MAKE (BRANDS} IN TOP 40 CITIE PER YEAR. 
```{r}
NEW_TABLE4 %>% 
 slice(1:40) %>%
ggplot (. , mapping = aes (x = City, y = n, color = Make)) + 
geom_point + 
facet_wrap (~ Model_Year) +
 labs (title = "Top Electric Vehicle Manufacturing Companies From 2013 to 2022" ) + 
  theme (axis.text.x=element_text (angle = -90, hjust = 0))
```

##```{r}
##ggplot(NEW_TABLE4, aes(x = City, y = n, color = Make)) + 
##  geom_point() + 
##  facet_wrap(~ Model_Year) +
##  labs(title = "Top Electric Vehicle Manufacturing Companies From 2013 to 2022") + 
##  theme(axis.text.x = element_text(angle = -90, hjust = 0))
##```

##To Check Weather Tesla has the Most Battery Electric Vehicle Cars.
```{r}
TABLE_CHECK <- Electric_Vehicle_Population_Data%>% count(Make, Electric_Vehicle_Type, sort=TRUE)
TABLE_CHECK
```

